Errata

### 2025-04-04 tex/Manuscript-1.tex
Update dissertation files with new packages and refine section headings

% NOTE: NO \documentclass, NO \begin{document}, NO \end{document} in this file!

@@

\begin{figure}[htbp] % You can adjust placement specifiers [htbp] as needed
    \centering % Center the content within the figure environment

    % --- Row 1 ---
    \begin{subfigure}[b]{0.48\textwidth} % Adjust width slightly less than 0.5 for spacing
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-01.png}
        \caption[]{} % Auto-label (a)
        \label{fig:m1_fig2_01}
    \end{subfigure}
    \hfill % Pushes the next subfigure to the right
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-02.png}
        \caption[]{} % Auto-label (b)
        \label{fig:m1_fig2_02}
    \end{subfigure}

    \vspace{0.5cm} % Add some vertical space between rows

    % --- Row 2 ---
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-03.png}
        \caption[]{} % Auto-label (c)
        \label{fig:m1_fig2_03}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-04.png}
        \caption[]{} % Auto-label (d)
        \label{fig:m1_fig2_04}
    \end{subfigure}

    \vspace{0.5cm}

    % --- Row 3 ---
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-05.png}
        \caption[]{} % Auto-label (e)
        \label{fig:m1_fig2_05}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-06.png}
        \caption[]{} % Auto-label (f)
        \label{fig:m1_fig2_06}
    \end{subfigure}

    \vspace{0.5cm}

    % --- Row 4 ---
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-07.png}
        \caption[]{} % Auto-label (g)
        \label{fig:m1_fig2_07}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-08.png}
        \caption[]{} % Auto-label (h)
        \label{fig:m1_fig2_08}
    \end{subfigure}

    \vspace{0.5cm}

    % --- Row 5 ---
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-09.png}
        \caption[]{} % Auto-label (i)
        \label{fig:m1_fig2_09}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-10.png}
        \caption[]{} % Auto-label (j)
        \label{fig:m1_fig2_10}
    \end{subfigure}

    \vspace{0.5cm}

    % --- Row 6 (Centered) ---
    % Since it's the only one on this line within the main \centering, it will be centered.
    \begin{subfigure}[b]{0.48\textwidth} % Width can be adjusted if needed
        \centering
        \includegraphics[width=0.8\linewidth]{img/M1-Figure_2-11.png} % Optional: make slightly narrower than others
        \caption[]{} % Auto-label (k)
        \label{fig:m1_fig2_11}
    \end{subfigure}

    % --- Main Caption and Label for the entire figure ---
    \caption{Mean and standard error of soil properties for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC) and Nahuelbuta (NA), without (BSC-) and with biocrust cover (BSC+), and the interaction of both factors. (EC = electrical conductivity, BD = bulk density, C\textsubscript{t} = total carbon, SOC = soil organic carbon, SIC = soil inorganic carbon, N\textsubscript{t} = total nitrogen, CN = carbon to nitrogen ratio). Significant factors include Tukey's Post-hoc-Test indicated by letters on the top of the bars. Different letters represent significant differences at p <0.05.}
    \label{fig:soil_properties_panel} % A descriptive label for the whole figure

>>>>

% NOTE: NO \documentclass, NO \begin{document}, NO \end{document} in this file!
\usepackage{subcaption} % Add this package for subfigure support

@@

\begin{figure}[htbp] % Adjust placement specifiers [htbp] as needed
    \centering % Center the entire block of subfigures

    % --- Row 1 (3 figures) ---
    \begin{subfigure}[b]{0.32\textwidth} % Width suitable for 3 across
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-01.png}
        % No caption or label needed here
    \end{subfigure}
    \hfill % Distribute space
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-02.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-03.png}
    \end{subfigure}

    \vspace{0.3cm} % Adjust vertical space between rows if needed

    % --- Row 2 (3 figures) ---
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-04.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-05.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-06.png}
    \end{subfigure}

    \vspace{0.3cm}

    % --- Row 3 (3 figures) ---
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-07.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-08.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-09.png}
    \end{subfigure}

    \vspace{0.3cm}

    % --- Row 4 (2 figures, centered) ---
    % Use slightly wider subfigures here, pushed apart by \hfill
    \begin{subfigure}[b]{0.48\textwidth} % Width suitable for 2 across
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-10.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{img/M1-Figure_2-11.png}
    \end{subfigure}

    % --- Main Caption and Label for the entire figure ---
    \caption{Mean and standard error of soil properties for Pan de Azúcar (PA), Santa Gracia (SG), La Campana (LC) and Nahuelbuta (NA), without (BSC-) and with biocrust cover (BSC+), and the interaction of both factors. (EC = electrical conductivity, BD = bulk density, C\textsubscript{t} = total carbon, SOC = soil organic carbon, SIC = soil inorganic carbon, N\textsubscript{t} = total nitrogen, CN = carbon to nitrogen ratio). Significant factors include Tukey's Post-hoc-Test indicated by letters on the top of the bars. Different letters represent significant differences at p <0.05.}
    \label{fig:soil_properties_panel} % Use the same descriptive label
